---
title: "Getting Started with binomial"
author: "Cloris Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial
The package "binomial" is a self-created implemenetation for calculating the binomial distribution given the number and probability of success in a fixed number of random trials performed, and to visualize such probability distribution.


## Calculates the number of combinations in which k successes can occur in n trials

For example, the number of combinations in which k = 2 successes can occur in n = 5 trials is 
```{r}
bin_choose(n = 5, k = 2)
```

## Calculate the probability of getting certain success in certain trials

For example, probability of getting 2 successes in 5 trials (assume the probability of success is 0.5)
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

## Compute the probability distribution
For example, binomial probability distribution of different successes in five trials (assume the probability of success is 0.5)
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
```

## Graph a barplot to display the probability histogram of a binomial distribution object "bindis"
```{r}
plot.bindis(dis1)
```
It gives us an visualization of the probabilities with a bar-graph to show the distribution for each success level given a constant number of trials. 

## Compute the probability distribution and the cumulative distribution
For example, binomial cumulative distribution of different successes in five trials (assume the probability of success is 0.5)
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
```

## Graph the cumulative distribution of an object "bincum"
```{r}
plot.bincum(dis2)
```
It gives us an visualization of the probabilities with a line-plot to show the cumulation of ascending success levels.

## Create binomial variable using given number of trials and successes
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```

## Obtain the summary of the binomial distribution with given trials and probability inputs

The `summary()` function will give you the full summary description of the object and the `print.summary()` function will give a nicely contents of the summary output

```{r}
summary.binvar(bin1)
```


## 
