---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is a self-created package for calculating the binomial distribution given the number and probability of success in a fixed number of random trials performed, and to visualize such probability distribution.

* `bin_choose()` calculates the number of combinations
* `bin_probability()` calculates the probability of getting successes
* `bin_distribution()` creates an object of class `bindis`cand compute the probability distribution
* `bin_cumulative()` creates an object of class `bincum` and compute the cumulative probability distribution 
* `bin_variable()` creates an object of class `binvar` and create binomial variable using given number of trials and successes
* `plot.bindis()`graphs a barplot to display the probability histogram of a binomial distribution object `bindis`
* `plot.bincum()` graphs the cumulative distribution of an object "bincum"
* `summary.binvar()`gives the full summary description of the object

## Helpful functions to calculate summary measures

* `bin_mean()` to calculate the mean.
* `bin_variance()` to calculate the variance.
* `bin_mode()` to calculate the most likely success number.
* `bin_skewness()` to measure the skewenss.
* `bin_kurtosis()` to calculate the kurtosis.

## Motivation

This package has been developed to help people understand and easily calculate binomial related things.


## Usage

```{r}
library(binomial)

# get the total combination number
bin_choose(n = 5, k = 2)

# get the binomial probability
bin_probability(success = 2, trials = 5, prob = 0.5)

# create the binomial distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1

# get the barplot of the probability histogram of a binomial distribution
plot.bindis(dis1)

# create the cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2

# get the line plot of cumulative probability distribution 
plot.bincum(dis2)


# get the binomial variables 
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1

# get the summary the binomial statistical elements
summary.binvar(bin1)

```

